Estimation below the detection limit

### 2018-04-24 TEX/draft2.tex
updates for Section 2

\author{Tamir Bendory}
\maketitle

@@

Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
A plain way to present the forward model is as a mixture of blind deconvolution problems between binary signals and the target signals
\begin{equation} \label{eq:model}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
\end{equation}
%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
Each  $s_i\in\{0,1\}^N$ is associated with the position of the occurrences of the corresponding $x_i$. Let $\mathcal{S}_i$ denotes the set of  the nonzero
 values of $x_i$ and assume that the all $\mathcal{S}_i$'s are disjoint. The union of supports is denoted by $s = \sum_{i=1}^Ks_i$ and similarly $\mathcal{S} = \cup \mathcal{S}_i$. 
The cardinality of the sets are denoted by $\vert \mathcal{S}_i\vert = M_i$ and $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.  Neither the $M_i$'s nor $M$ are assumed to be known.

In order to estimate the mixture of signals autocorrelations, we assume that the support of $s$ is not clustered. In particular, 
\begin{equation} \label{eq:spacing}
\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
\end{equation}
The goal of the problme is to estimate $x_1,\ldots,x_K$ from $y$.

Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. 
To make the problem well-posed, we must  assume some prior knowledge or  structure. 
In our case, the prior information is that $s$ is a binary signal that satisfies~\eqref{eq:spacing}. 
Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
where the focus is on high $\SNR$ regimes.

An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s. The  $s_i$'s  are referred to as \emph{nuisance  variables}. Indeed, in many blind deconvolution applications the sole purpose is to estimate one of the unknown signals. For instance, in image deblurring, both the blurring
kernel and the high-resolution image are unknown, but the primary goal is only
to sharpen the image.

If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{de2012exact,duval2015exact,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating $s$ is impossible. To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$. That is to say, we get a series of windows, each one contains a signal at unknown location. 
Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
However, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}. Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$. As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals themselves, despite the impossibility of detecting their individual occurrences.

For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
\begin{eqnarray}
y = x\ast w + \varepsilon,  
\end{eqnarray} 
where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
The goal of this problem is to estimate $x$ (identify the system). The question of identifiability of $x$ under
this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
model in the  case of a single signal ($K = 1$).

Likelihood-based methods seek to maximize the likelihood function for $x$,
given the observed signal $y$. Solving this optimization exactly is typically
intractable, and so heuristic methods are used instead. One proposed heuristic
 is to use Markov Chain Monte Carlo (MCMC); in special
cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
The EM method is based upon a certain ``forward-backward'' procedure
used in hidden Markov models, described in~\cite{rabiner1989tutorial}. \TODO{We need to explain}
Other problems solve for parameterized models of $x$; for instance, see~\cite{andrieu2001bayesian}. 
That same paper also considers multiple distinct signals $x$, as in our heterogeneity framework ($K>1$). Their proposed
solution is an MCMC algorithm designed for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based
on recovery from moments and cumulants, which are akin to our method, have
also been previously used for system identification. The question of identifiability
of $x$ from third-order statistics with non-Gaussian $w$ was considered in~\cite{lii1982deconvolution}. \TODO{how is it different from bispectrum inversion?}
Methods using the third- and fourth-order cumulants are described in~\cite{giannakis1989identification,tugnait1984identification}.

>>>>

\author{Tamir Bendory, Nicolas Boumal, William Leeb and Amit Singer}
\maketitle

@@

Let $x_1,\ldots,x_K\in\RL$ be the sought signals and let $y\in\RN$ be the data. 
The forward model can be posed as a mixture of \emph{blind deconvolution} problems between binary signals and the target signals $x_i$:
\begin{equation} \label{eq:model}
y = \sum_{i=1}^K x_i\ast s_i + \varepsilon,\quad \varepsilon\sim\mathcal{N}(0,\sigma^2 I).
\end{equation}
%We model the background information as i.i.d.\ Gaussian noise with zero mean and $\sigma^2$ variance. 
The nonzero values of each  $s_i\in\{0,1\}^N$ determine the position of the occurrences of the corresponding $x_i$. 
We denote the set of these nonzero values by 
 $\mathcal{S}_i$ and its cardinality by $\vert \mathcal{S}_i\vert = M_i$. 
By assuming that all $\mathcal{S}_i$'s are disjoint,  we let $s = \sum_{i=1}^Ks_i$, $\mathcal{S} = \bigcup_{i=1}^{K} \mathcal{S}_i$ and  $\vert \mathcal{S}\vert :=M =  \sum_{i=1}^{K}M_i$.  Neither the $M_i$'s nor $M$ are assumed to be known.

In order to estimate the mixture of autocorrelations, we assume that the support of $s$ is not clustered. In particular,
\begin{equation} \label{eq:spacing}
\text{For all }  i,j\in\mathcal{S}, \, i\neq j,  \quad  \vert i-j \vert\geq L-1.  
\end{equation}
The goal of the problem is to estimate $x_1,\ldots,x_K$ from $y$.

Blind deconvolution is a longstanding problem, arising in a variety of engineering and scientific applications, such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. 
To make the problem well-posed, we must  assume some prior knowledge or  structure. 
In our case, the prior information is that $s$ is a binary signal that satisfies the separation constraint~\eqref{eq:spacing}. 
Other settings of blind deconvolution problems have been analyzed recently, see for instance~\cite{ahmed2014blind,li2016identifiability,li2016rapid,ling2015self,ling2017blind,chi2016guaranteed}
where the focus is on high $\SNR$ regimes.

An important feature of the problem under consideration is that while both $x_i$'s and $s_i$'s are unknown, the goal is merely to estimate the $x_i$'s. The  $s_i$'s  are referred to as \emph{nuisance  variables}. Indeed, in many blind deconvolution applications the sole purpose is to recover one of the unknown signals. For instance, in image deblurring, both the blurring
kernel and the high-resolution image are unknown, but the primary goal is only
to sharpen the image.

If $x$ is known and $K=1$, then a sparse signal can be estimated by linear programming  in the high $\SNR$ regime, e.g.,~\cite{azais2015spike,denoyelle2017support,bendory2016robust,bendory2017robust,bernstein2017deconvolution}. However, in the low $\SNR$ regime, estimating the binary sparse signal $s$ is impossible. To see that, suppose that an oracle provides us $M$ windows of length $W>L$, each contains one copy of $x$. That is to say, we get a series of windows of length $W$, each one contains a signal at an unknown location. 
Estimating the position of the known signal within each  window is an easier problem than detecting the support of $s$. 
Nevertheless, even this problem is impossible in the low $\SNR$ regime~\cite{aguerrebere2016fundamental}. Therefore, we conclude that detecting the nonzero values of $s$ is impossible in low $\SNR$. As aforementioned, this work focuses on this regime and examines under what conditions we can estimate the signals, despite the impossibility of detecting their individual occurrences.

For $K=1$, our problem can be also interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
\begin{eqnarray}
y = x\ast w + \varepsilon,  
\end{eqnarray} 
where $x$ is the unknown signal (``system''), $w$ is an unknown, random, input sequence and $\varepsilon$ is an additive noise.   
%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under
this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}.
In the special case where $w\in\{0,1\}^N$, satisfying the spacing requirement~\eqref{eq:spacing}, we obtain our
model in the  case of a single signal ($K = 1$).

Likelihood-based methods seek to maximize the likelihood function for $x$,
given the observed signal $y$. Solving this optimization exactly is typically
intractable, and thus heuristic methods are used instead. One proposed technique is to use Markov Chain Monte Carlo (MCMC); in special
cases, including the case where $w$ is binary, EM has been used~\cite{cappe1999simulation}.
The EM method is based upon a certain ``forward-backward'' procedure
used in hidden Markov models~\cite{rabiner1989tutorial}. \TODO{need further explanation, is it an approximation?}.
Another paper considers parameterized models for multiple distinct signals, as in our heterogeneity framework ($K>1$)~\cite{andrieu2001bayesian}.
Their proposed solution is an MCMC algorithm tailored for their specific parametrized problem.

Because likelihood methods are computationally expensive, methods based
on recovery from moments, which are akin to our method, have
also been previously used for system identification. The question of identifiability
of $x$ from third-order statistics with non-Gaussian $w$ was considered in~\cite{lii1982deconvolution}. \TODO{how is it different from bispectrum inversion?}
Methods based on the third- and fourth-order moments are described in~\cite{giannakis1989identification,tugnait1984identification}.
